Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/results-devices.tex
continue incorporating comments, upto 4.2

\begin{table}[t]
\begin{center}
\begin{tabular}{| c | r | r |}
\hline
 Misbehavior &  Cubetastic3000 & Smartphone \\
 \hline
 \hline
 All & 58.79\% & 46.67\%\\
 \hline
Vibration & 14.81\%  &  6.14\%\\
Bluetooth & 44.12\%  &  19.86\%\\
Unmuted Call & 87.10\%  &  58.44\%\\
Screenshot & 52.78\%  & 55.74\%\\
Premium Calls/Texts & 86.49\%  &  91.94\%\\ 
\hline
\end{tabular}
\caption{VURs for the five questions about device misbehaviors described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
\label{deviceVUR}
\end{center}
\end{table}

\subsubsection{Device}
Recall that each participant answered 2 questions drawn from a set of 5 regarding their reactions to smartphone misbehaviors. To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same 5 questions amongst the pool of 293 Cubetastic3000 scenarios, only modifying the device type. In this manner, while all 1,782 participants received 2 smartphone questions, there were 159 participants who received at least one of these questions in relation to the Cubetastic 3000. Across all participants, the VUR was 46.7\% (of 1,782) when describing smartphones, whereas the VUR increased to 58.8\% (of 159) when describing these same misbehaviors on the Cubetastic3000. The VURs for both devices for all 5 questions are in Table ~\ref{deviceVUR}.

To preserve data independence, we performed a Mann-Whitney U test by comparing participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants). We found this difference to be statistically significant ($108,664.0$, $p<0.0005$), however, the effect size was incredibly small ($r=0.08$). Because of this small effect size, we did not further reduce our statistical power by separately comparing each of the 5 misbehaviors. As a result, we can conclude that in general users are likely to be more wary of misbehaviors occurring on wearable devices than smartphones, the difference is likely negligible. Similarly, the entire effect may be due to participants' increased familiarity with smartphones, and therefore may disappear as they increasingly encounter more wearable devices.

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{| c | r | r |}
\hline
 Misbehavior &  Cubetastic3000 & Smartphone \\
 \hline
 \hline
 All & 58.79\% & 46.67\%\\
 \hline
Vibration & 14.81\%  &  6.14\%\\
Bluetooth & 44.12\%  &  19.86\%\\
Unmuted Call & 87.10\%  &  58.44\%\\
Screenshot & 52.78\%  & 55.74\%\\
Premium Calls/Texts & 86.49\%  &  91.94\%\\ 
\hline
\end{tabular}
\caption{VURs for the five questions about device misbehaviors described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
\label{deviceVUR}
\end{center}
\end{table}

\subsubsection{Device}
Recall that each participant answered 2 questions drawn from a set of 5 regarding their reactions to smartphone misbehaviors. To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same 5 questions amongst the pool of 293 Cubetastic3000 scenarios, only modifying the device type. In this manner, while all 1,782 participants received 2 smartphone questions, there were 159 participants who received at least one of these questions in relation to the Cubetastic 3000. Across all participants, the VUR was 46.7\% (of 1,782) when describing smartphones, whereas the VUR increased to 58.8\% (of 159) when describing these same misbehaviors on the Cubetastic3000. The VURs for both devices for all 5 questions are in Table \ref{deviceVUR}.

To ensure independence of observations, we performed a Mann-Whitney U test to compare participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants). This difference was statistically significant ($U=108,664.0$ with $p<0.0005$), however, the effect size was very small ($r=0.08$). Because of this small effect size, we did not further reduce our statistical power by separately comparing each of the 5 misbehaviors. We conclude that while in general users are likely to be more wary of misbehaviors occurring on wearable devices than smartphones, the difference is likely negligible. The entire effect may be due to participants' increased familiarity with smartphones, and therefore may disappear as they increasingly encounter more wearable devices.

### 2015-03-06 tex-inputs/results-recipient.tex

\subsubsection{Data Recipient}
There was a statistically significant difference in VUR for data sent to an application's servers compared to data sent to human recipients. On average, 42\% of participants stated that they would be ``very upset'' if their data was shared with only an application's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}). A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}). However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios. But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results. Similarly, we are unaware of a more appropriate test, given our data format. Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed). Nonetheless, we repeated our analysis using only one randomly-selected data point per participant and found that our selected test was robust to this violation. Therefore, we conclude that participants were significantly more concerned about having their data seen by a human versus an application, though differences between specific human groups such as the public, friends, and work contacts were not as significant.

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
\label{recipient-chi}
\end{center}
\end{table}

>>>>

\subsubsection{Data Recipient}
There was a statistically significant difference in VUR for data sent to an application's servers compared to data sent to human recipients. On average, 42\% of participants stated that they would be ``very upset'' if their data was shared with only an application's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were almost double (Table \ref{recipient-vur}). A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}). However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios with multiple recipients. But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results. Similarly, we are unaware of a more appropriate test, given our data format. Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed). Nonetheless, we repeated our analysis using only one randomly-selected data point per participant and found that our selected test was robust to this violation. Therefore, we conclude that participants were significantly more concerned about having their data seen by a human versus an application, though differences between specific human groups such as the public, friends, and work contacts were not as significant.

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
\label{recipient-chi}
\end{center}
\end{table}
